Generalized Social Dynamics in Human-Robot Interaction

### 2017-04-20 paper.tex
New focus: social dynamics beyond task specifics

\title{The robot who pretend-played with me}

@@

@@

\begin{itemize}
    \item Can I have real fun playing with my robot?
    \item A Robot Which is Fun to Play With: Leveraging AI to Participate in Complex
        Social Situations
    \item A Window Onto Your Mind: Playful Robots Leveraging Attention to
        Predict Actions
    \item Playing Like your Friend: Dealing with the High Dimensionality of
        Real-World Social Dynamic

@@

focus on abstract socio-cognitive facets (robot
perception and manipulation are simplified); well suited for qualitative and
quantitative analysis using metrics like Słowinski’s Individual Motor Signature
(for behavioural alignment), Ballard’s coding of children’s free-play
interactions, with-me-ness (for assessment of co-engagment).

@@

    %%% NODES
    \node [node] (mentalrepresentations) {Mental Representations};
    \node [above left=of mentalrepresentations] (gameactions) {game actions};
    \node [node, above left=of gameactions] (gamedynamics) {Game dynamics};
    \node [above right=of mentalrepresentations] (socialactions) {social actions};
    \node [node, above right=of socialactions ] (socialdynamics) {Social Dynamics};

@@

Protoimperative vs protodeclarative pointing~\cite{baron1986perceptual}

>>>>

\title{Generalized Social Dynamics in Human-Robot Interaction}

@@

Relying on free play as a prototypical open task, we investigate the social
dynamics of children dyads playing together. By analyzing them from the
perspective of artifical socio-cognition and human-robot interaction, we
evidence key social patterns and show that robots can recognise them,
interpret them, and (where applicable) generate them in a task-agnostic
fashion. By subsequently reusing these social patterns in similar
child-robot free play situations, we show a significant increase of the
interaction duration.

@@

\begin{itemize}
    \item The robot who pretend-played with me
    \item I Guess Your Next Move! Leveraging Social Cues for Robots to
        Understand Free-play Situations
    \item A Robot Which is Fun to Play With: Leveraging AI to Participate in Complex
        Social Situations
    \item A Window Onto Your Mind: Playful Robots Leveraging Attention to
        Predict Actions
    \item Playing Like your Friend: Dealing with the High Dimensionality of
        Real-World Social Dynamic
    \item A Robot Which Adapts its Social Behaviour to its Partner's Age

@@

focus on abstract socio-cognitive facets (robot
perception and manipulation are simplified); well suited for qualitative and
quantitative analysis using metrics like Słowinski’s Individual Motor Signature
(for behavioural alignment), Anderson's~\cite{anderson2004social} coding of children’s free-play
interactions, with-me-ness (for assessment of co-engagment).

@@

    %%% NODES
    \node [node] (mentalrepresentations) {Mental Representations};
    \node [above left=of mentalrepresentations] (gameactions) {\it game actions};
    \node [node, above=of gameactions] (gamedynamics) {Game dynamics};
    \node [above right=of mentalrepresentations] (socialactions) {\it social actions};
    \node [node, above=of socialactions ] (socialdynamics) {Social Dynamics};

@@

Protoimperative vs protodeclarative pointing~\cite{baron1989perceptual}
